### 2020-06-03 1_introduction.tex
Apply Pat's comments.

Existing approaches to this problem focus on \emph{proxy-}/\emph{mini-apps}
or \emph{microbenchmarks}. These smaller codes distill key
computational characteristics of larger applications: mini-apps are
often derived from a larger code, and thus inherit some subset of its
properties, while benchmarks are typically chosen to reflect a more
narrow set of behaviors. In either case, while a variety of insight
can be gained, the overall programming effort required is proportional to the
product of the number of systems and behaviors being
evaluated. Few published studies compare more than a
handful of systems~\cite{LULESH13, Deakin19}.

>>>>

Existing approaches to this problem focus on \emph{proxy-}/\emph{mini-apps}
or \emph{microbenchmarks}. These smaller codes distill key
computational characteristics of larger applications: mini-apps are
often derived from a larger code, and thus inherit some subset of its
properties, while benchmarks are typically chosen to reflect a more
narrow set of behavior(s). In either case, while a variety of insight
can be gained, the overall programming effort required is proportional to the
product of the number of systems and behaviors being
evaluated. Few published studies compare more than a
handful of systems~\cite{LULESH13, Deakin19}.

### 2020-06-03 2_task_bench.tex
Fiddle with figure size.
Apply Pat's comments.

@@

The Task Bench core library is fully validating. {\color{blue} The output of each
task is a tuple (time step, column) and is unique within a task
graph. All inputs are verified by checking the expected dependencies
against those received, and an assertion is thrown if validation
fails. These checks ensure that every execution of Task Bench is
correct. Note that the graph representation is concise, making these
checks very inexpensive.} An evaluation of the performance impact of
validation showed it to be less than 3\% at the smallest task
granularities in any Task Bench implementation, with a negligible
effect on overall results.

>>>>

The Task Bench core library is fully self-validating: {\color{blue} The output of each
task is a tuple $\langle \textrm{row, col}\rangle$ and is unique for a given task
graph. Inputs are verified by checking the expected dependencies
against those received, and an assertion is thrown if validation
fails. These checks ensure that every execution of Task Bench is
correct. Note that the graph representation is concise, making these
checks very inexpensive.} An evaluation of the performance impact of
validation showed it to be less than 3\% at the smallest task
granularities in any Task Bench implementation, with a negligible
effect on overall results.

@@

### 2020-06-03 5_evaluation.tex
Tweaks for space.
Apply Pat's comments.

Most systems for HPC are highly scalable,
but this is not true of all the systems included in this
evaluation. Lower is better in Figure~\ref{fig:metg-compute}, and
flat is ideal. Lines that rise with node count indicate less than
ideal scaling. Most notably, Spark is primarily
intended for industrial data center applications with task
granularities measured in seconds. Spark uses a centralized
controller, which limits throughput, and this is visible in the figure
as the line for Spark immediately rises with node count. Keep in mind
that Spark is being evaluated here with a non-trivial dependence
pattern that is relatively unrepresentative of Spark's normal use
cases. Spark is more efficient with trivial parallelism, as described
in Section~\ref{subsec:number-of-dependencies}.

@@

One advantage of asynchronous execution is
the ability to mitigate load imbalance with little or no additional programmer effort, especially in the presence of
task parallelism. To quantify this effect,
Figure~\ref{fig:efficiency-imbalance} plots task granularity vs
efficiency under load imbalance where each task's duration is multiplied by a uniform random variable in [0,~1). Task durations are generated with a deterministic
pseudo random number generator with a consistent seed to ensure
identical durations for all systems.

@@

The remaining differences are due primarily to
different scheduling behaviors. The execution of 4
simultaneous task graphs only partially mitigates the
load imbalance between tasks. Systems that provide an
additional on-node work stealing capability (such as Chapel with the distrib scheduler) see additional gains in
efficiency at large task granularities. However, the use of
work-stealing queues can also impact throughput at small task
granularities. For example, Chapel's default (non-work-stealing) scheduler outperforms Chapel distrib at very small task granularities. We do not consider Charm++ load balancers because the imbalance is \emph{non-persistent} (i.e., timestep $t$ is uncorrelated with timestep $t+1$). We leave analysis of persistent load imbalance to future work.
}

>>>>

Most systems for HPC are highly scalable,
but this is not true of all the systems included in this
evaluation. Lower is better in Figure~\ref{fig:metg-compute}, and
flat is ideal. Lines that rise with node count indicate less than
ideal scaling. Most notably, Spark is primarily
intended for industrial data center applications with task
granularities measured in seconds. Spark uses a centralized
controller, which limits throughput, and this is visible in the figure
as the line for Spark immediately rises with node count. Keep in mind
that Spark is being evaluated here with a nontrivial dependence
pattern that is relatively unrepresentative of Spark's normal use
cases. Spark is more efficient with trivial parallelism, as described
in Section~\ref{subsec:number-of-dependencies}.

@@

One advantage of asynchronous execution is
the ability to mitigate load imbalance with little or no additional programmer effort, especially in the presence of
task parallelism. To quantify this effect,
Figure~\ref{fig:efficiency-imbalance} plots task granularity vs.
efficiency under load imbalance where each task's duration is multiplied by a uniform random variable in [0,~1). Task durations are generated with a deterministic
pseudo random number generator with a consistent seed to ensure
identical durations for all systems.

@@

The remaining differences are due primarily to
different scheduling behaviors. The execution of 4
simultaneous task graphs only partially mitigates the
load imbalance between tasks. Systems that provide an
additional on-node work stealing capability (such as Chapel with the \texttt{distrib} scheduler) see additional gains in
efficiency at large task granularities. However, the use of
work-stealing queues can also impact throughput at small task
granularities. For example, Chapel's default (non-work-stealing) scheduler outperforms \texttt{distrib} at very small task granularities. We do not consider Charm++ load balancers because the imbalance is \emph{non-persistent} (i.e., timestep $t$ is uncorrelated with timestep $t+1$). We leave analysis of persistent load imbalance to future work.
}

### 2020-06-03 8_case_study.tex
Rename case study section.
Apply Alex's edits.
Apply Pat's comments.

\section{Case Study}
\label{sec:case-study}

@@

Chapel uses a naive round-robin scheduler by default, which can lead
to unexpected load balance issues because certain language features
(such as remote array assignment) implicitly generate tasks. This
resulted in poor peak performance, even at large task granularities,
which in some cases made it impossible to measure METG (because peak
efficiency did not exceed 50\%). Chapel's other schedulers add
overhead, resulting in higher METGs. We worked around this issue with
\lstinline{serial}.

PaRSEC uses task pruning to reduce analysis work performed on each
node, and thus improve scalability at large node
counts. Initial Task Bench results achieved less than the expected
scalability: METG was rising too quickly with node count.  The PaRSEC
developers diagnosed this as a bug in task pruning---the optimization was failing to trigger---and it was
subsequently fixed. We also implemented a version of the PaRSEC code,
\lstinline{shard}, which uses manual pruning to demonstrate that
additional gains may still be possible.

>>>>

\section{Performance Issues Discovered}
\label{sec:case-study}

@@

Chapel uses a naive round-robin scheduler by default, which can lead
to unexpected load balance issues because certain language features
(such as remote array assignment) implicitly generate tasks. This
resulted in poor peak performance, even at large task granularities,
which in some cases made it impossible to measure METG (because peak
efficiency did not exceed 50\%). Chapel's other schedulers add
overhead, resulting in higher METGs. We worked around this with
a \lstinline{serial} block.

PaRSEC uses task pruning to reduce analysis work performed on each
node, and thus improve scalability at large node
counts. Initial Task Bench results achieved less than the expected
scalability: METG was rising too quickly with node count.  The PaRSEC
developers diagnosed a bug in task pruning---the optimization was failing to trigger---and it was
subsequently fixed. We also implemented a version of the PaRSEC code,
\lstinline{shard}, which uses manual pruning to demonstrate that
additional gains may still be possible.
